Estimating the Performance of Entity Resolution Algorithms: New Approach and a Case Study at PatentsView.org

### 2022-08-23 paper/main.tex
Updates from Overleaf

\title{Practical Performance Evaluation of Entity Resolution Algorithms: Lessons Learned at PatentsView.org}

@@

Pairwise precision and recall metrics were first reported in \cite{Newcombe1959}, with \cite{Bilenko2003} and \cite{Christen2007} emphasizing the importance of precision-recall curves for algorithm evaluation. However, there are issues with the use of pairwise precision and recall in entity resolution applications, such as the large relative importance of large clusters. As such, other clustering metrics have been proposed, including cluster precision and recall, cluster homogeneity and completeness, and generalized merge distances \citep{Michelson2009, Menestrina2010, Maidasani2012, Barnes2015}. Important practical issues regarding the use of aggregate metrics are discussed in \cite{Hand2018}.

@@

\bibliographystyle{chicago}
\bibliography{biblio}

>>>>

\title{Estimating the Performance of Entity Resolution Algorithms: New Approach and a Case Study at PatentsView.org}

@@

Pairwise precision and recall metrics were first reported in \cite{Newcombe1959}, with \cite{Bilenko2003} and \cite{Christen2007} emphasizing the importance of precision-recall curves for algorithm evaluation. However, there are issues with the use of pairwise precision and recall in entity resolution applications, such as the large relative importance of large clusters. As such, other clustering metrics have been proposed, including cluster precision and recall, cluster homogeneity and completeness, the B$^3$ metric \citep{bagga1998algorithms}, and generalized merge distances \citep{Michelson2009, Menestrina2010, Maidasani2012, Barnes2015}. Important practical issues regarding the use of aggregate metrics are discussed in \cite{Hand2018}.

@@

\nocite{Subramanian2021}
\bibliographystyle{chicago}
\bibliography{biblio}
